A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-20 04_Severity_MetaAnalysis.Rmd
simplify correction of neg values to once

# Correct Inf to 0
PM_dat_D[PM_dat_D$yi_log == -Inf,"yi_log"] <- 0
PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001

@@

hist(PM_dat_D$yi_logit)
PM_dat_D$vi_logit <-
   (PM_dat_D$vi_percent) /
   (PM_dat_D$yi_percent * (1 - PM_dat_D$yi_percent)) ^ 2

# Correct -Inf to zeros
PM_dat_D[PM_dat_D$yi_logit == -Inf,"yi_logit"] <- 0.001
PM_dat_D[PM_dat_D$vi_logit == -Inf,"vi_logit"] <- 0.001
```

>>>>

# Correct Inf to 0
PM_dat_D[is.na(PM_dat_D$yi_log),"yi_log"] <- 0
PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001

@@

# logit transformed variance
PM_dat_D$vi_logit <-
   (PM_dat_D$vi_percent) /
   (PM_dat_D$yi_percent * (1 - PM_dat_D$yi_percent)) ^ 2

# Correct -Inf to zeros
PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0.000
